\vskip-0.6in \Large Political Uncertainty

### 2015-10-08 GS-extension.tex
add bordered Hessian and conditions for two non-negative bribes case
add one principal minor condition to SOC section

>>>>

\vskip.5in
The SOCs when one non-negativity constraint binds; bordered Hessian is 4x4. \\
		\begin{tabular}{cccc}
			0 & $\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial g_1}{\partial b\left(-0\right)}$ & $\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ \\
			$\frac{\partial g_1}{\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
			$\frac{\partial g_1}{\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
			$\frac{\partial g_1}{\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
		\end{tabular} \\

\vskip.2in		
Evaluating the constraint terms:\\
\begin{tabular}{cccc}
			0 & -1 & 0 & 0 \\
			-1 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)^2}$ & $\frac{\partial^2 L}{\partial b(0)\partial b\left(-\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(-\frac{1}{2}\right)}$  \\
			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(0\right)}$ & $\frac{\partial^2 L}{\partial b(0)^2}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)\partial b\left(0\right)}$ \\
			0 & $\frac{\partial^2 L}{\partial b\left(-\frac{1}{2}\right)\partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b(0) \partial b\left(\frac{1}{2}\right)}$ & $\frac{\partial^2 L}{\partial b\left(\frac{1}{2}\right)^2}$
		\end{tabular}

The second order condition is on the last two principal minors. The largest must be negative. The next to last should then be positive.
\begin{itemize}
	\item First we need the determinant of the next-to-last principal minor, the 3x3 matrix that is the upper-lefthand corner of this matrix. This determinant should be positive. We can use the trick by which one copies the first two rows to the right of the matrix and then multiplies down the columns to the right and up the columns to the right (these terms get a negative sign). Then the determinant is
	  \[
		  0 + 0 + 0 - \left[0 + 0 + (-1)(-1)\frac{\partial^2 L}{\partial b(0)^2} \right] = - \frac{\partial^2 L}{\partial b(0)^2}
		\]
		Because we need this to be positive, we need $\frac{\partial^2 L}{\partial b(0)^2} < 0$. This corresponds to the $X$ compositive variable, and happens only when $X$ is positive.
\end{itemize}
